\begin{frame}
\textbf{Annex}
\end{frame}

\begin{frame}{Other nonlinear filtering methods in macroeconomics}
\label{details_lit}
\begin{wideitemize}
\item Boehl (2021) proposes a promising and very fast piecewise-linear solution algorithm.
\item Farmer (2021) provides a fast nonlinear approximation of the likelihood in non-Gaussian state space
models. 
\item Aruoba et al. (2020) exploit the piecewise-linear nature of OBCs for high-order solution
and particle filtering. 
\item These methods are particularly suitable for low-dimensional state-spaces but are
difficult to scale to models with more state variables.
\item For Markov-switching models, Maih (2015) provides efficient perturbation methods.
\end{wideitemize}
\hyperlink{lit}{\beamerbutton{Back}}
\end{frame}


\begin{frame}{PKF: Initialization}
\label{details_pkf_init}
\begin{wideitemize}
    \item Given the initial state mean and variance $x_0$ and $\mathbf{P}_0$, we denote their `best' estimate at any time $t-1$ $x_{t-1|t-1}, \mathbf{P}_{t-1|t-1}.$	
    \item Notation for state-dependent matrices: 
    \begin{eqnarray*}
    \mathbf{T}_{t|t}&=& \mathbf{T}(x_{t-1},\varepsilon_{t}) \\
    \mathbf{C}_{t|t}&=& \mathbf{C}(x_{t-1},\varepsilon_{t}) \\
    \mathbf{R}_{t|t} &=& \mathbf{R}(x_{t-1},\varepsilon_{t}),
    \end{eqnarray*}
\item Initialize the guess of the updated state matrices for iteration $j=0$
\begin{eqnarray*}
\mathbf{T}^{j}_{t|t}&=&\mathbf{T}_{t|t-1} \\
\mathbf{R}^{j}_{t|t}&=&\mathbf{R}_{t|t-1} \\
\mathbf{C}^{j}_{t|t}&=&\mathbf{C}_{t|t-1}. 
\end{eqnarray*}
\item Superscript $j$ denotes the iteration to find the state matrices.
\end{wideitemize}
\hyperlink{pkf_init}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{PKF: Standard prediction and update step}
	\label{details_pred_upd}
\begin{itemize}
\item Given the guessed matrices, perform a prediction step
\begin{align*}
x^{(j)}_{t|t-1}&=\mathbf{T}^{(j-1)}_{t|t}\cdot x_{t-1|t-1}+\mathbf{C}^{(j-1)}_{t|t} \\
\mathbf{P}^{(j)}_{t|t-1}&=\mathbf{T}^{(j-1)}_{t|t}\cdot \mathbf{P}_{t-1|t-1}\cdot \mathbf{T'}^{(j-1)}_{t|t} +\mathbf{R}^{(j-1)}_{t|t}\cdot \mathbf{Q}\cdot \mathbf{R'}^{(j-1)}_{t|t}\\
y^{(j)}_{t|t-1}&=\mathbf{H} x^{(j)}_{t|t-1}\\
\mathbf{F}^{(j)}_{t}&=\mathbf{H}\cdot \mathbf{P}^{(j)}_{t|t-1}\cdot \mathbf{H}'\\
v^{(j)}{t}&= z_t-y^{(j)}_{t|t-1} 
\end{align*}
\item and an update step
\begin{eqnarray*}\label{eq:update1}
\mathbf{K}^{(j)}_t  &=&  \mathbf{P}^{(j)}_{t|t-1}\cdot\mathbf{H}'\\
x^{(j)}_{t|t} &=& x^{(j)}_{t|t-1}+\mathbf{K}^{(j)}_t \left(\mathbf{F}^{(j)}_{t}\right)^{-1}v^{(j)}_t  \nonumber\\ 
\mathbf{P}^{(j)}_{t|t} &=& \mathbf{P}^{(j)}_{t|t-1}-\mathbf{K}^{(j)}_t\left(\mathbf{F}^{(j)}_{t}\right)^{-1} {\mathbf{K}^{(j)}}'_t. \nonumber
\end{eqnarray*}
\item Here, each iteration $j$ follows the standard Kalman recursion.
\end{itemize}
	\hyperlink{pkf_pred_upd}{\beamerbutton{Back}}
\end{frame}




